Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

Therefore, the workflow that must be carried out by the performance regression analysis (PRA) system is as follows:
\begin{enumerate}
	\item The system must be able to detect when there is a regression in Microservice-based applications
	\item The system must be able to determine the source or root cause of the regression after it is detected
\end{enumerate}\textbf{}

>>>>

Therefore, the workflow that must be carried out by the performance regression analysis (PRA) system is as follows:
\begin{enumerate}
	\item The system must be able to detect when there is a regression in Microservice-based application
	\item The system must be able to determine the source or root cause of the regression after it is detected
\end{enumerate}

Seeing the needs of the PRA system above, from the several approaches in the subchapter, the authors assess
There are two approaches that can be used, namely the Cumulative Analysis approach on
II.4.2 and Aggregation and Correlation Analysis approach in II.4.3.
